Parameter precision in economic growth models inspired by Ecological Economics

### 2015-10-09 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Fix misspelling.
Edits to framing.

  \item Also, inspired by Ayres and Warr, 
        we don’t want to assume elasticity of substitution 
        of unity as CD does.
        (What does Linex give for the elasticity of substitution between factors of production?)

@@

    \item Ayres and Warr used a non-standard production function.
          Will their insights hold true for standard production functinos like Cobb-Douglas and CES?

@@

  \item Standard approaches assume normal distributions for model parameters. 
        In the non-linear world of CES, 
        those assumptions aren't appropriate. 
        Need a new approach in the non-CD world.

@@

\end{itemize}
%
This paper explores and justifies those choices by
%
\begin{enumerate}

  \item comparing standard techniques and our approaches for the Cobb-Douglas production function and

  \item applying our techniques to the CES production production function.

>>>>

  \item Also, inspired by Ayres and Warr, 
        we don't want to assume elasticity of substitution 
        of unity as CD does.
        (What does Linex give for the elasticity of substitution between factors of production?)

@@

    \item Ayres and Warr used a non-standard production function.
          Will their insights hold true for standard production functions like Cobb-Douglas and CES?

@@

  \item Non-linear fitting has several complications in the fitting process.

  \item Furthermore, standard approaches to determining parameter precision 
        for linear and non-linear fitting
        assume normal distributions for model parameters. 
        In the non-linear world of CES, 
        those assumptions aren't appropriate. 
        Need new approaches in the non-CD world.

@@

\end{itemize}
%
This paper explores and justifies those choices by:
%
\begin{enumerate}

  \item comparing standard techniques and our approaches for estimating parameter precision
        for the Cobb-Douglas production function, and

  \item applying our advanced techniques for parameter estimation
        (including precision)
        to the CES production production function.
